Supplementary Figure 2c

### 2017-11-20 inst/stable_line_ccnd1_prot/stable_line_ccnd1_prot.Rmd
adding full WB for CCND1

_Representative experiment_
```{r, out.width = "500px"}

url <- "stable_line_ccnd1_prot/stable_line_ccnd1_prot_singleExp.png"
knitr::include_graphics(file.path(projectUrl, url))

@@

<div class="caption">
A resulting western blot representative of the results from the three independant experiments.
</div>

>>>>

_Western blot_
```{r, out.width = "500px"}

url <- "stable_line_ccnd1_prot/stable_line_ccnd1_prot.png"
knitr::include_graphics(file.path(projectUrl, url))

@@

<div class="caption">
The resulting western blot showing the results from the three independant experiments.
</div>
